Graphics

### 2020-06-02 individual-cohorts/graphics_t_statistics.Rmd
fix heatmap

---
title: "Graphics"
author: "KM"
date: "5/18/2020"
output: html_document
---

@@

```{r heatmapa, fig.width = 5, fig.height = 5 }
for_fig <- dplyr::select(df_one, -Comparison)
colnames(for_fig) <- gsub(" t-statistic", "", colnames(for_fig))

cor <- corr.test(for_fig, use = "pairwise.complete.obs", method = "spearman")

@@

```{r heatmapb, fig.width = 5, fig.height = 5 }
for_fig <- dplyr::select(df_two, -Comparison)
colnames(for_fig) <- gsub(" t-statistic", "", colnames(for_fig))

cor <- corr.test(for_fig, use = "pairwise.complete.obs", method = "spearman")

@@

```{r heatmapc, fig.width = 5, fig.height = 5 }
for_fig <- dplyr::select(df_three, -Comparison)
colnames(for_fig) <- gsub(" t-statistic", "", colnames(for_fig))

cor <- corr.test(for_fig, use = "pairwise.complete.obs", method = "spearman")

>>>>

---
title: "Graphics"
author: "KM"
date: "`r date()`"
output: html_document
---

@@

```{r heatmapa, fig.width = 5, fig.height = 5 }
colnames(df_one) <- gsub(" t-statistic", "", colnames(df_one))

cor <- corr.test(df_one, use = "pairwise.complete.obs", method = "spearman")

@@

```{r heatmapb, fig.width = 5, fig.height = 5 }
colnames(df_two) <- gsub(" t-statistic", "", colnames(df_two))

cor <- corr.test(df_two, use = "pairwise.complete.obs", method = "spearman")

@@

```{r heatmapc, fig.width = 5, fig.height = 5 }
colnames(df_three) <- gsub(" t-statistic", "", colnames(df_three))

cor <- corr.test(df_three, use = "pairwise.complete.obs", method = "spearman")
